\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\begin{document}

\begin{center}
CMPT 434 Proposal \\
Matthew Munro, mam552, 11291769 \\
Xianglong Du, xid379, 11255352 \\
Timofei Kabakov, tik981, 11305645 \\
\end{center}
\pagebreak

Our project will involve creating a cross-platform static C library intended to 
abstract away platform-specific implementation details. This means the application programmer would never have to directly 
include or call platform-specific header files such as sys/socket.h or winsock.h. Instead, they would write their program by 
linking to the static library and using an API defined by us. \\

The project will include an example program showcasing how to use the library. It will involve multiple windows clients 
communicating with a linux server implementing the Administrator model, where the server will have a dedicated thread for handling requests 
and farm blocking operations off to worker threads. \\

Potential challenges include learning Windows' Winsock API. This will give us an opportunity to learn more about 
how different operating systems handle network programming. \\

The project will also include a test runner to test a number of unit tests to ensure correctness as well as consistency across the two platforms. \\

We will have succeeded in the objectives of the implementation project if we are able to write the example program fully utilizing our 
cross-platform library without any need for directly using platform-specific APIs. 
\end{document}